The pollination trade-off

### 2018-09-17 paper/manuscript.Rmd
Adjust discussion
Close #22

* We found that animal pollination only brings a small amount of extra conspecific pollen (compared to selfing) if any. This relatively small difference is probably very important though because crossing has been shown to be evolutionary better than cloning in the long term. 
* The relationship between conspecific and heterospecific pollen is positive which indicates than net facilitation is the dominant outcome. This agrees with previous findings. However the amount of added conspecific pollen is in average smaller than the amount of added heterospecific pollen.
* Despite finding that facilitation is the most common outcome. We also were able to find clear signature of competition for pollinators at the community level.
* We found that, as assumed in pollination models, the mutualistic benefit is modulated by the species degree and therefore there is indeed evidence for a trade-off. Moreover, the trade off does not depend on the species or the community. Which is a good thing because we tend to simplify models by assuming a common trade-off for the whole community.
* However the mutualistic benefit was not just modulated by the degree but other factors also played significant roles. 
* These factors, in particular the plant relative abundance, was important at explaining the differences between plants. 
* We found that models performed better when explanatory variables were constructed so that they take into account information across all the communities in which a species was present. This means that despite the particularities of each community (random effects acounted for a large proportion of the variance) we can still predict general outcomes by knowing some general traits about the plant species and how it relates to other plants in their community.

Understanding what makes species and communities different is important not only because of its ecological and evolutionary implications. 
It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree. 
The extent to which species degree affects the benefit is called *mutualistic trade-off*. 
This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
At the same time it is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly. 
Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities, empirical evidence is scarce, to say the least.

It is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.

At the community scale, understanding the costs of sharing mutualistic partners at the community scale is important not only because of its ecological and evolutionary implications. It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners—the species degree. 
The extent to which species degree affects the benefit is called mutualistic trade-off. This approach,
37 considerably simplifies the mathematical treatment of competition for pollinators. At the same time it is
38 based on the intuitive rationale that a species that interacts with few species benefits strongly from each
39 of them, whereas a species that interacts with a large number of species does so comparatively weakly.
40 Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity
41 of mutualistic communities, empirical evidence is scarce, to say the least.

At the community scale other factors we would expect

Here, we explore the signatures competition for pollinators in diverse natural communities, where empirical data is more scarce.

Here we examine the signature, at the community scale, that sharing mutualistic partners has in the quality and quantity of pollination. 
Although seeimgly a simple question, teasing appart the signature of this "trade-off" has been elusive in part because of the large amounts of data required. 
Most studies that have examined competition for pollinators are based the pollen deposited on flower stigmas. 
However

All together, existing studies at the community scale show that, as expected, the effective result of sharing mutualistic partners, in most cases, one of facilitation. 
We hipothezise that 
Recent empirical evidence suggest that the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly. 
However, they also show a large variability in this result—both across species and across communities. 
One of the most intuitive drivers of the variability in competition, and therefore widely used in theoretical models of mutualism to account for the neggative effects of mutualism, is the species degree---the number of mutualistic partners. 
It is based on the intuitive rationale 
 that other factors might also play an important role shaping the competition for pollination.

First, we estimate the gain on pollen that can be attributed to the mutualistic interactions. 
Second, we investigate wether there is a relationship between this gain and a a suite of variables that together describe the role of the plant species and the ecological context. 
Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
**TODO: Mini conclusion here**

>>>>

* We did find a trade-off between the number of partners a species interacts with and the mutualistic service. Interacting with more species alone is often accompained by a decreasse in both the quantity and quality of pollination. 
* However, the effect and importance of this trade-off is comparatively small when considering other factors that describe the species niche and its ecological settings. 
* We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any. This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their pollen gets deposited on the stigma. Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favors cross-pollination as, evolutonary, it has been shown to be a better strategy than cloning. 
* Overal it seems like density seems to be a dominant force behind pollen transfer. If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is relfected in a smaller amount of deposited pollen. We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen. 
* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree. 
This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
However we show that care must be taken because the neggative effects of the mutualistic trade-off in both the quantity and quality of pollinaton can be offset by density mechanisms. Species with large degrees also tend be abundant and prolific pollen producers.
